---
title: "Covid-19 Vaccination Report"
author: "Angella Kim, Danika Lee, Lifan Liao, Shunshun Yao"
date: "2021/5/20"
output: html_document
---

```{r include=FALSE}
library("knitr")
raw_df <- na.omit(read.csv("data/us_state_vaccinations.csv"))
source("script/aggregated_table.R")
source("script/Chart 1.R")
source("script/Chart 2.R")
source("script/Chart 3.R")
source("script/summary.R")
```

```{r include=FALSE}
summary <- summary_info(raw_df)
```


### Introduction
Our problem domain revolves around the topic of COVID-19 and vaccination
statistics. We are interested in this field/domain because there are many
aspects of COVID-19 that are important to track. Data on vaccinations can help
track the current situation of COVID-19, and as more and more people get
vaccinated, data on this topic can allow us to know of a rough estimate as to
how things will be like in the future. The disease has taken over the world,
and in the United States we have seen the harsh impacts of the disease.
Displaying vaccination statistics is a sign of hope that our lives will soon go
back to normal. I downloaded the data from this link, on [Kaggle](https://www.kaggle.com/paultimothymooney/usa-covid19-vaccinations).
This data set is collected by Our World in Data, and they collected data about
the current U.S residents and the vaccines distributed. As of May 9th, there are
`r nrow(raw_df)` observations and `r ncol(raw_df)` features.


Since our data set revolves around the COVID-19 vaccine statistics from each
state in the U.S, the summary information that we calculated shows the average
population of each state in the U.S, which is `r as.integer(summary$mean_pop)`. The average total people
vaccinated in each state is `r as.integer(summary$mean_total)`. Using those two pieces of information, we were
able to get the average percentage of vaccinated people per state compared to the number
of residents, which turned out to be `r summary$avg_percent_pplpop`%. For further analysis,
the mean for total vaccines in each state was `r as.integer(summary$mean_vac)`, making the average percentage of
people vaccinated compared to the number of vaccines available per state `r summary$avg_percent_pplvac`%.


### Table intro

This table contains aggregated Covid-19 vaccination information of 51 states in the US by May 9th, 2021. This table is grouped by states. The final number of vaccination by May 9th, 2021 and the mean daily vaccination are calculated, so that it is easy to compare the progress of Covid-19 vaccination between states. 

The table is sorted descending by the amount of total vaccination.

- California has the most vaccination by May 9th, 2021.
- California has the largest amount of vaccine distributed by May 9th, 2021.


```{r echo=FALSE}
kable(aggregated_table(raw_df))
```


## Summary Charts

### Chart 1


```{r echo=FALSE}
chart_1(raw_df)
```
- Chart 1 displays the total number of people that got vaccinated per state up until May 9th, 2021. 
- Bar chart was used to help visualize the comparison of amount of vaccinated people among different states and identify states with the most vaccinated population and states with the lowest vaccinated population.

### Chart 2

```{r echo=FALSE, warning=FALSE}
chart_2(raw_df)
```

- Chart 2 compares the population of each state with its vaccinated population up until May 9th, 2021. 
- The grouped bar graph indicates the estimated amount of people who have not got their vaccination in each state and visually demonstrates the gap between total population and total vaccinated population on a state-wide level.

### Chart 3

```{r echo=FALSE, warning=FALSE}
chart_3(raw_df)
```

- Chart 3 compares each state's total population with its calculated average daily vaccination given to the public up until May 9th, 2021.
- The scatter plot graph helps establish a visible trend where readers can examine the relationship between each state's total population and calculated average daily vaccination given to the public.


