---
title: "Covid-19 Vaccination Report"
author: "Lifan Liao","Danika Lee","Angella Kim","Shunshun Yao"
date: "2021/5/20"
output: html_document
---

```{r include=FALSE}
library("knitr")
raw_df <- na.omit(read.csv("data/us_state_vaccinations.csv"))
source("script/aggregated_table.R")
source("script/Chart 1.R")
source("script/Chart 2.R")
source("script/Chart 3.R")
```


## Summary Table

### Table intro

This table contains aggregated Covid-19 vaccination information of 51 states in the US by May 9th, 2021. This table is grouped by states. The final number of vaccination by May 9th, 2021 and the mean daily vaccination are calculated, so that it is easy to compare the progress of Covid-19 vaccination between states. 

The table is sorted descending by the amount of total vaccination.

- California has the most vaccination by May 9th, 2021.
- California has the largest amount of vaccine distributed by May 9th, 2021.


```{r echo=FALSE}
kable(aggregated_table(raw_df))
```

## Summary Charts

### Chart 1

```{r echo=FALSE}
chart_1(raw_df)
```

- Chart 1 displays the total number of people that got vaccinated per state up until May 9th, 2021. 
- Bar chart was used to help visualize the comparison of amount of vaccinated people among different states and identify states with the most vaccinated population and states with the lowest vaccinated population.

### Chart 2

```{r echo=FALSE}
chart_2(raw_df)
```

- Chart 2 compares the population of each state with its vaccinated population up until May 9th, 2021. 
- The grouped bar graph indicates the estimated amount of people who have not got their vaccination in each state and visually demonstrates the gap between total population and total vaccinated population on a state-wide level.

### Chart 3

```{r, echo=FALSE}
chart_3(raw_df)
```

- Chart 3 compares each state's total population with its calculated average daily vacccination given to the public up until May 9th, 2021.
- The scatter plot graph helps establish a visible trend where readers can examine the relationship between each state's total population and calculated average daily vacccination given to the public.
